\documentclass[line,margin]{res}
    \usepackage[none]{hyphenat}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \begin{document}
\name{{\LARGE Daniel T Rust}}
\address{danieltuckerrust@gmail.com | 404-386-7807 | Grand Forks, ND | github.com/trustdan | linkedin.com/in/rustd}

\begin{resume}
	\vspace{-5mm}
	        
	\section{Work Experience}
	\textbf{US Air Force}, {\sl Innovation, Acquisitions Officer}\hfill 09/2020 | Present\\Grand Forks AFB, ND\\\begin{itemize} \itemsep 3pt
	\item Company idea man, divergent thinking.  Inspired very popular ChatGPT app.
	\item Causing people to innovate more, but better though.  Inspiring YouTube videos.
	\item Safety trained and certified to investigate flight mishaps.
	\item RQ-4 Global Hawk pilot with an emphasis on radar and moving target indicators.
	\item Strong psychological safety and diversity advocate in Fortify the Force.
	\end{itemize}
	\textbf{US Air Force}, {\sl Judge Advocate}\hfill 05/2017 | 09/2020\\Barksdale AFB, LA\\\begin{itemize} \itemsep 3pt
	\item Investigate and try criminal courts-martial.  "Crime Dog" moniker given.
	\item Prosecute civilians in the Shreveport federal courthouse for Barksdale AFB.
	\item Senior supervisory attorney: \textquotedbl{}Best legal researcher I\textquotesingle{}ve known.\textquotedbl{}
	\end{itemize}
	\textbf{AmeriCorps VISTA}, {\sl Volunteer in Service to America}\hfill 06/2013 | 06/2014\\Chattanooga, TN\\\begin{itemize} \itemsep 3pt
	\item Outreach, putting assistive technology in the hands (or possession of) veterans.
	\item Started Signal Centers' Google for Nonprofits account, apps for veterans.
	\end{itemize}
	\section{Education}
	\textbf{Vermont Law School}, {\sl Accelerated Juris Doctor} \hfill 08/2014 | 12/2016\\South Royalton, VT\\\\
	\textbf{Berry College}, {\sl BA in International Studies} \hfill 08/2009 | 12/2012\\Mt Berry, GA
	\section{Skills, Certifications}
	\begin{tabular}{@{}ll}
		\textbf{Counter-fraud}:            & CFE, CAMS, CFCS certified.  CIA, audit, in progress. \\
		\textbf{Law}:                      & Inactive licenses in TX, MA, MO. \\
		\textbf{Open Source Intelligence}: & Gathered tools to find a missing person / family friend. \\ 
		                                   & Go-to guy when you need the goods. \\
		\textbf{Divergent ideation}:       & Bringing very profitable ideas to table. \\
	\end{tabular}
	\section{Projects}
	\textbf{Innovat.io}, {\sl a future webapp powered by Anthropic, inspiring defense innovation, as:}\\ 
	\textnormal https://github.com/trustdan/awesome-sbir-sttr/\\
	\textbf {Admitchu.com,} \textquotedbl{}Admitting chu to your top schools.\textquotedbl{} \\
	\textbf {First} useful and popular international relations Android app. \\ 
	\textbf {Finance app} that led to Samsung calling from Korea, forming a partnership. \\
	\section{Clearances}
	\textbf{Top Secret / Sensitive Compartmented Information}, {\sl USG} \hfill 08/2020 \\
	\textbf{Trusted} with the Nation\textquotesingle{}s top secrets. \\
	
	\hfill{\sl References available upon request.} \\
\end{resume}
\end{document}